### 2024-08-22 skripsi/bab2.tex
wip ch 2 & 3

\section{Least Squares Support Vector Machine}
\noindent An arguably fundamental model widely used whether in pedagogical settings or otherwise is the support vector machine. It dates back to works by Vapnik \& Lerner in 1963 (Recognition of Patterns with help of Generalized Portraits) and V. N. Vapnik \& A. Ya. Chervonenkis in 1964 (A note on one class of perceptrons/On a perceptron class). As the development on SVM continued, what originally was a model for classification of separable data generalized to regression tasks as well Vapnik (2000 The Nature of Statistical Learning Theory).

>>>>

\section{Least Squares Support Vector Machine}
\noindent An arguably fundamental model widely used whether in pedagogical settings or otherwise is the support vector machine. It dates back to works by Vapnik \& Lerner in 1963 (Recognition of Patterns with help of Generalized Portraits) and V. N. Vapnik \& A. Ya. Chervonenkis in 1964 (A note on one class of perceptrons/On a perceptron class). As the development on SVM continued, what originally was a model for classification of separable data generalized to regression tasks as well Vapnik (2000 The Nature of Statistical Learning Theory). 
\subsection{Disadvantages}
However, the main disadvantage of LSSVMs are the fact that they do not have the sparse property of SVMs which can leave performance on the table. A simple mitigation can be done by filtering training samples with small absolute values of lagrangian multipliers \autocite{haifengwangComparisonSVMLSSVM2005}.
